Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
addressed a part of the comments

\todo{The following paragraph has been already stated above. Let us clarify this is a useful repetition to recap things?}

The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be set to zero.

When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I_c,F_c\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.

@@

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach (described in Sec.~\ref{sec:CEGIS-precision-incrementation})
  uses a multi-staged verification phase and performs solution generalisation based on
the plant precision, the number of loop unrollings, 
and the sampling rate. Essentially, it finds a controller for an individual initial state
and input with a bounded time horizon and generalises to all states,
inputs, and time horizons. %% (with a final verification loop that verifies
%% the continuous system behaviour against the previously verified
%% discrete system bi-simulation)
\item[2.] The second approach (described in Sec~\ref{sec:CEGIS-abstraction-refinement})
  %% uses abstract acceleration to compute the set of reachable states,
  %% which enables it to perform abstraction refinement inside the CEGIS loop.
  finds a controller for a continuous initial set of states and input set, 
  over an abstraction of the continuous dynamics that conforms to witness proofs at specific times; 
  it further generalises the solution over all times by refining the number of witnesses.  \todo{clarify use of abstract acceleration. add references.}
\end{itemize}

@@

% Let us recall the formulas used for single-input and single-output (SISO) systems 
% in sections \ref{sec:reachable} and \ref{sec:observable}.
% A controllable system with quantization will have the following dynamics:
% \todo{eliminate vectors}
% %
% \begin{align}
% \label{eq:observer_LTI_cf}
% \vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
% \end{align}
% \begin{align*}
% \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
% \mat{B}_{tp}=&\mat{T}\mat{B}_d&
% \mat{B}_{tn}=&\mat{T}\mat{B}_d&
% \mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
% \end{align*}

% \begin{align*}
% \mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
% \begin{array}{ccccc}
% 0&1&0&\cdots&0\\
% 0&0&1&\cdots&0\\
% \vdots&\vdots&\vdots&\ddots&\vdots\\
% 0&0&0&\cdots&1\\
% k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
% \end{array}\right]
% \label{eq:cf_SISO_2}
% \end{align*}

% The characteristic polynomial of the above matrix is:
% %
% \begin{align*}
% z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
% \end{align*}

% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
\todo{where is $\phi_{input}$ defined?}
Once we have established convergence, we may examine the 
specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
% Whilst there are other properties, we may include in the verification, 
% we will solely focus on these for simplicity of the explanation.
% We assume that we do not want saturation in our system, 
% hence the control loop has only one mode.

>>>>

% \todo{The following paragraph has been already stated above. Let us clarify this is a useful repetition to recap things?}

At this point, we recap the the synthesis problem that we solve in this work:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be set to zero.  
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I_c,F_c\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.

@@

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach (described in Sec.~\ref{sec:CEGIS-precision-incrementation})
  uses a multi-staged verification phase and performs solution generalisation based on
the plant precision, the number of loop unrollings, 
and the sampling rate. Essentially, it finds a controller for an individual initial state
and input with a bounded time horizon and generalises to all states,
inputs, and time horizons. The safety check is performed in this approach 
via unfolding of the transition system corresponding to the synthesised controller.

%% (with a final verification loop that verifies
%% the continuous system behaviour against the previously verified
%% discrete system bi-simulation)
\item[2.] The second approach (described in Sec~\ref{sec:CEGIS-abstraction-refinement})
  finds a controller for a continuous initial set of states and input
  set, over an abstraction of the continuous dynamics that conforms to
  witness proofs at specific times; it further generalises the
  solution over all times by refining the number of witnesses.  
  In order to perform the safety check, this approach uses abstract acceleration
  \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
  %\todo{clarify use of abstract acceleration. add references.}
\end{itemize}

@@

Let us recall the formulas used for single-input and single-output (SISO) systems 
in sections \ref{sec:reachable} and \ref{sec:observable}.
A controllable system with quantization will have the following dynamics:
\todo{eliminate vectors}
%
\begin{align}
\label{eq:observer_LTI_cf}
\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
\end{align}
\begin{align*}
\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
\mat{B}_{tp}=&\mat{T}\mat{B}_d&
\mat{B}_{tn}=&\mat{T}\mat{B}_d&
\mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
\end{align*}

\begin{align*}
\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
\begin{array}{ccccc}
0&1&0&\cdots&0\\
0&0&1&\cdots&0\\
\vdots&\vdots&\vdots&\ddots&\vdots\\
0&0&0&\cdots&1\\
k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
\end{array}\right]
\label{eq:cf_SISO_2}
\end{align*}

The characteristic polynomial of the above matrix is:
%
\begin{align*}
z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
\end{align*}

For a stabilized closed-loop, which is necessary for our safety property, we need
these roots to remain within the unit circle, which we verify using Jury's criteria.
Notice that in our polynomials $c_0=1$ and we only use reals.
\todo{where is $\phi_{input}$ computed?}
Once we have established convergence, we may examine the 
specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
% Whilst there are other properties, we may include in the verification, 
% we will solely focus on these for simplicity of the explanation.
% We assume that we do not want saturation in our system, 
% hence the control loop has only one mode.
